---
title: "AE 02"
subtitle: "Flint Water Crisis"
date: "Due: August 21, 11:59PM"
author: "YOUR NAME GOES HERE"
output: 
  html_document: 
    toc: TRUE
    toc_float: TRUE
    fig_height: 4
    fig_width: 9
---

## Introduction

The data set consists homes sampled with three water lead contaminant values at
designated time points. The lead content is in parts per billion (ppb). 
Additionally, some location data is given about each home.

First, let's load in the `tidyverse` with the following code:

```{r load-packages, warning = FALSE, message=FALSE}
library(tidyverse)
library(shiny)
library(rvest)
```

To get started, read in the `flint.csv` file using the function `read_csv`. Note
that this function is part of the `tidyverse`, which you must load *before*
attempting to use the function (if it's not loaded, the function won't work!).

```{r flint, warning = FALSE, message = FALSE}
demo <- read_csv("Tellus-Boost-FB-UA-2021-Demo-Feb-9-2021-to-Apr-19-2021.csv")
geo <- read_csv("Tellus-Boost-FB-UA-2021-Geo-Feb-9-2021-to-Apr-19-2021.csv")
imp <- read_csv("Tellus-Boost-FB-UA-2021-Imp-Device-Feb-9-2021-to-Apr-19-2021.csv")
```


Let's preview the data with the `glimpse()` function:

```{r glimpse-data, echo = TRUE}
glimpse(demo)
glimpse(geo)
glimpse(imp)
view(demo)

```
```{R demo-project}

alt_demo <- demo %>% group_by(`Ad Name`)%>%mutate( total = sum(`Amount Spent (USD)`)) 
alt_demo <- alt_demo %>% group_by(`Ad Name`)%>%mutate(objcount = (sum(`Unique Link Clicks`+ `Unique Landing Page Views`, na.rm = T)))%>% mutate(Effectiveness = objcount/total)
short <- alt_demo %>% select(`Ad Name`, Effectiveness)

v <- short %>% distinct()%>% arrange(desc(Effectiveness))%>%filter(!is.na(Effectiveness))

ggplot(v, mapping = aes(x =`Ad Name`, y= Effectiveness))+ geom_bar(stat="identity", xlab="Ad Name",
        ylab="Effectiveness")

```


```{r geo-project}
altgeo <- geo %>% group_by(`DMA Region`)%>%mutate(objcount = (sum(`Unique Link Clicks`+ `Unique Landing Page Views`, na.rm = T)))%>%mutate(test = sum(Impressions))%>% mutate(effective_regions = objcount/test)


v1 <- altgeo %>%filter(effective_regions >= 0)%>%arrange(desc(effective_regions))
short1 <- v1 %>% select(`DMA Region`,effective_regions)%>% distinct()
ggplot(short1, mapping = aes(x =`DMA Region`, y= effective_regions))+ geom_bar(stat="identity", xlab="Region",
        ylab="Effectiveness")
#add code later to look by average rent of the locations.
#possible map of the locations by the number of people 

```

```{r demo}

altimp<- imp %>% group_by(`Impression Device`,Platform,Placement)%>%mutate(Impressionsc = sum(`App Installs`,na.rm =T)/sum(Impressions,na.rm =T)*sum(`Amount Spent (USD)`))

summary<- altimp %>% select(`Impression Device`,Platform,Placement,Impressionsc)%>%distinct()%>%arrange(Impressionsc)%>%filter(Impressionsc !=0)

```